They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-11 paper.tex
More paper tweaks

\imfigB{PolarVector1}{The basics of PolarVector}

@@

The mutation function in Figure 8 essentially creates a new copy of the current genome, nudged by normally distributed random numbers.

@@

\imfigB{ZombieAgentUpdateNearby}{The portion of the FixedUpdate method for
determining the position of nearby objects relative to a Zombunny}

@@

\imfig{ZombieAgentUpdateMovement}{The function of FixedUpdate for handling
  movement between ticks}

@@

The ZombieAttacker class (see Figure 19) calls Update on each tick, dealing damage to any item
in toAttack, which is a HashSet of Targetable GameObjects that intersect with
a Zombunny's attack collider (see Figure 4). This way, a Zombunny can attack
multiple GameObjects so long as they intersect with its attack collider. Damage
is applied to items in toAttack by calling their individual takeDamage methods,
with the damage dealt as determined by the Zombunny's genome passed as a
parameter.

@@

\subsection{Evolution}

In \

@@

At this time, we are waiting on actual results from our project.
We hope that given a large enough population of zombies, we might see
populations of zombies evolving to counteract players' strategies. Evolution
will likely have little trouble tackling a trivial or consistent player
strategy, like rebuilding the same towers in the same place and
relying heavily on a single tower type, but may have trouble keeping
up with a player that constantly changes strategy over the course of the game.
Our system of softmaxing the genome speed, health, and damage could also
result in progressively larger values relative to the mutation rate, making it
hard for long-evolved high speed value to be traded for damage in the face of
changing player strategies.

@@

Sexual (genderless) reproduction could also be introduced as a way of trying to
increase diversity. Plain sexual reproduction without any further restrictions
could allow good traits that evolve in parallel to be combined into a single
individual with the benefits of both, which has fairly obvious advantages.
This simple approach to sexual reproduction could, however, force a single
species to dominate quickly depending on how well neural net parameters combine,
as it could easily be the case that two disparately evolving neural nets combine
into a total dud, despite having fit parents. One way around that would be to
condition reproduction on similarity, such genomes are more likely to reproduce
with those that are structurally similar. Another approach would be to allow
genomes to determine mating preference based on other genomes' content and
fitness, and then run them through a tournament to determine mates. This would
have the additional benefit of allowing additional emergent behavior that has
not been conceived of in this speculation.

>>>>

%figure 5%
\imfigB{PolarVector1}{The basics of PolarVector}

@@

The mutation function in Figure 8 essentially creates a new copy of the current genome, which is then nudged by normally distributed random numbers.

@@

\imfigH{ZombieAgentUpdateNearby}{The portion of the FixedUpdate method for
determining the position of nearby objects relative to a Zombunny}

@@

\imfig{ZombieAgentUpdateMovement}{The function of FixedUpdate that handles
  movement between ticks}

@@

The ZombieAttacker class (see Figure 19) calls Update on each tick, dealing damage to any item
in toAttack, which is a HashSet of Targetable GameObjects that intersect with
a Zombunny's attack collider (see Figure 4). This way, a Zombunny can attack
multiple GameObjects so long as they intersect with its attack collider. Damage
is applied to items in toAttack by calling their individual takeDamage methods.
Damage dealt is determined by the Zombunny's genome, and is passed as a parameter 
to takeDamage.

@@

\subsection{Genetic Algorithm}

In \tavs,

@@

At this time, we are waiting on actual results from our project.
We hope that given a large enough population of Zombunnies, we might see
populations of Zombunnies evolving to counteract players' strategies. Evolution
will likely have little trouble tackling a trivial or consistent player
strategy, like rebuilding the same towers in the same place and
relying heavily on a single tower type, but may have trouble keeping
up with a player that constantly changes strategy over the course of the game.
Our system of softmaxing the genome speed, health, and damage could also
result in progressively larger values relative to the mutation rate, making it
hard for long-evolved high speed value to be traded for damage in the face of
changing player strategies.

@@

Sexual (genderless) reproduction could also be introduced as a way of trying to
incentivize diversity. Plain sexual reproduction without any further restrictions
could allow good traits that evolve in parallel to be combined into a single
individual with the benefits of both, which has fairly obvious advantages.
This simple approach to sexual reproduction could, however, force a single
species to dominate quickly depending on how well neural net parameters combine,
as it could easily be the case that two disparately evolving neural nets combine
into a total dud, despite having fit parents. One way around that would be to
condition reproduction on similarity, such genomes are more likely to reproduce
with those that are structurally similar. Another approach would be to allow
genomes to determine mating preference based on other genomes' content and
fitness, and then run them through a tournament to determine mates. This would
have the additional benefit of allowing emergent behavior that has not been 
conceived of in this speculation.
